### 2019-05-28 draft_charts.Rmd
Edits through the morning of 2019-05-28

#' rename_cohort
#'
#' @param x a vector with cohorts
#'
#' @return a vector of renamed cohorts
rename_cohort <- function(x) {
  cohort <- list("1936-1945" = "Pre-boomers (1936–45)", 
                 "1946-1955" = "Early boomers (1946–55)", 
                 "1956-1965" = "Late boomers (1956–65)", 
                 "1966-1975" = "Gen Xers (1966–75)", 
                 "1976-1985" = "Early Millenials (1976-1985)")

  if (is.null(cohort[[x]])) {
    print("ERROR: no cohort match")
    stop()
  } else {
    return(cohort[[x]])
  }
}

rename_cohort <- function(x, two_lines = TRUE) {
  if (two_lines == TRUE) {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers\n(1936–45)", 
      `1946-1955` = "Early boomers\n(1946–55)", 
      `1956-1965` = "Late boomers\n(1956–65)", 
      `1966-1975` = "Gen Xers\n(1966–75)", 
      `1976-1985` = "Early millenials\n(1976-1985)")

    factor(cohort, levels = c("Pre-boomers\n(1936–45)", 
                              "Early boomers\n(1946–55)", 
                              "Late boomers\n(1956–65)", 
                              "Gen Xers\n(1966–75)", 
                              "Early millenials\n(1976-1985)"))
  } else {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers (1936–45)", 
      `1946-1955` = "Early boomers (1946–55)", 
      `1956-1965` = "Late boomers (1956–65)", 
      `1966-1975` = "Gen Xers (1966–75)", 
      `1976-1985` = "Early millenials (1976-1985)")

    factor(cohort, levels = c("Pre-boomers (1936–45)", 
                              "Early boomers (1946–55)", 
                              "Late boomers (1956–65)", 
                              "Gen Xers (1966–75)", 
                              "Early millenials (1976-1985)"))
  }
}

@@

```{r chart1}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent_format(accuracy = 0.1)(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("An Increasing Share of Retirees Won't Replace Pre-Retirement Incomes"),
      subtitler("Age 70 percentage of people who fail to replace 75% of age 50-59 earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2, 2, 30, 1, 1))
```

### 80% replacement rate

```{r chart1b}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Age 70 Percentage of People Who Fail to Replace 80% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2, 30, 1, 1))
```

### 85% replacement rate

```{r chart1c}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Age 70 Percentage of People Who Fail to Replace 85% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2, 30, 1, 1))
```

### 90% replacement rate

```{r chart1d}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%", "85-90%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Age 70 Percentage of People Who Fail to Replace 90% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 30, 1, 1))
```

### 100% replacement rate

```{r chart1e}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%", "85-90%", "90-95%", "95-100%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Age 70 Percentage of People Who Fail to Replace 100% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 30, 1, 1))
```

@@

```{r chart2}
chart2 <- read_csv("data/figure2.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, ncharts_aftertax_income_P50)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::dollar(ncharts_aftertax_income_P50, largest_with_cents = 0)), 
            vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Retirement Incomes are Increasing"),
      subtitler("Median age-70, per-capita, price-adjusted shared annuitized income less taxes"),
      chart2,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

@@

```{r, chart3}
chart3b <- read_csv("data/figure3b.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Male",
                       `2.Female` = "Female")) %>%  
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, Ownssb_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(Ownssb_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.75), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("The Gender Gap in Social Security Benefits is Narrowing"),
      subtitler("Median Age-70 Price-Adjusted Social Security Benefits by Sex"),
      chart3b,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 2, 30, 1, 1))
```

@@

```{r chart4}
chart4 <- read_csv("data/figure4.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Male",
                       `2.Female` = "Female")) %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(male)) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, lifetime_earn_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(lifetime_earn_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 1), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Growth in Earnings, Especially by Women, Will Boost Future Retirement Incomes"),
      subtitler("Median price-adjusted earnings from ages 25 to 69 at age 70 by sex"),
      chart4,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 2, 30, 1, 1))
```

@@

# create the output plot
plotr(titler("Racial and Ethnic Disparities in Retirement Income Will Persist"),
      subtitler("Age-70, per-capita, price-adjusted, shared annuitized income less taxes by race and ethnicity"),
      chart6,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

## Chart 7: Social Security Is a Pillar of Retirement Security {.tabset}

@@

### Arrangement 1

@@

read_csv("data/figure7.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(doby = rename_cohort(doby, two_lines = FALSE)) %>% 
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(as.character(nchartQuin), income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~doby) +
  labs(title = "Major Sources of Income at Age 70 by Income Quintile",
       x = "Income quintile",
       y = NULL) +
  remove_ticks()  
```

### Arrangement 2

```{r chart7-alt}
incomes <- c("Other income", "Financial income", "DB pension income", "Earnings", "Social Security")

chart7 <- read_csv("data/figure7.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(doby, income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~as.character(nchartQuin)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# create the output plot
plotr(titler("Social Security Is a Pillar of Retirement Security"),
      subtitler("Major sources of income at age 70 by income quintile"),
      chart7,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

@@

scheduled <- read_csv("data/figure1.csv") %>%
  mutate(law = "Scheduled law")

payable <- read_csv("data/figure9.csv") %>%
  mutate(law = "Payable law") %>%
  rename(ncharts_reprate = ncharts_reprate_payable)

chart9 <- bind_rows(scheduled, payable) %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby, law) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ungroup() %>%
  mutate(law = factor(law, levels = c("Scheduled law", "Payable law"))) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, rep_rate_threshold, fill = law)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), 
            vjust = -1,
            position = position_dodge(width = 0.8)) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Social Security Insolvency Will Damage Retirement Security"),
      subtitler("Age 70 Percentage of People Who fail to Replace 75% of Age 50-59 Earnings"),
      chart9,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

@@

```{r, chart12}
chart12 <- read_csv("data/figure12.csv") %>%
  filter(doby %in% cohorts) %>%
  rename(`Scheduled law` = ncharts_pov_Mean, 
         `Payable law` = ncharts_pov_payable_Mean) %>%
  gather(key = "law", value = "poverty", -doby, -Obs) %>%
  mutate(law = factor(law, levels = c("Scheduled law", "Payable law"))) %>%
  ggplot(aes(doby, poverty, fill = law)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::percent_format(accuracy = 0.1)(poverty)), 
            vjust = -1,
            position = position_dodge(width = 0.8)) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Social Security Insolvency Will Increase Poverty"),
      subtitler("Percentage of people in poverty at age 70"),
      chart12,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

@@

## Chart 11

```{r}
read_csv("data/figure11.csv") %>%
  mutate(year = doby + 70,
         insolvency_delta = (ncharts_income_payable - ncharts_income) / ncharts_income,
         quintile = cut(lifetime_earn, 5)) %>%
  ggplot(aes(lifetime_earn, ncharts_reprate)) +
  geom_point(alpha = 0.01)

>>>>

#' rename_cohort
#'
#' @param x a vector with cohorts
#'
#' @return a vector of renamed cohorts
rename_cohort <- function(x, two_lines = TRUE) {
  if (two_lines == TRUE) {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers\n(1936–1945)", 
      `1946-1955` = "Early boomers\n(1946–1955)", 
      `1956-1965` = "Late boomers\n(1956–1965)", 
      `1966-1975` = "Gen Xers\n(1966–1975)", 
      `1976-1985` = "Early millennials\n(1976-1985)")

    factor(cohort, levels = c("Pre-boomers\n(1936–1945)", 
                              "Early boomers\n(1946–1955)", 
                              "Late boomers\n(1956–1965)", 
                              "Gen Xers\n(1966–1975)", 
                              "Early millennials\n(1976-1985)"))
  } else {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers (1936–1945)", 
      `1946-1955` = "Early boomers (1946–1955)", 
      `1956-1965` = "Late boomers (1956–1965)", 
      `1966-1975` = "Gen Xers (1966–1975)", 
      `1976-1985` = "Early millennials (1976-1985)")

    factor(cohort, levels = c("Pre-boomers (1936–1945)", 
                              "Early boomers (1946–1955)", 
                              "Late boomers (1956–1965)", 
                              "Gen Xers (1966–1975)", 
                              "Early millennials (1976-1985)"))
  }
}

#' to_ordinal
#'
#' @param x translate numeric integers into ordinal numbers in a character vector 
#'
#' @return
#' @export
#'
#' @examples to_ordinal(1:30)
to_ordinal <- function(x, capitalize = FALSE, as_factor = FALSE) {
  # case_when(x %in% 11:13 ~ paste0(x, "th"),
  #           x %% 10 == 0 ~ paste0(x, "th"),
  #           x %% 10 == 1 ~ paste0(x, "st"),
  #           x %% 10 == 2 ~ paste0(x, "nd"),
  #           x %% 10 == 3 ~ paste0(x, "rd"),
  #           x %% 10 %in% 4:9 ~ paste0(x, "th"),
  #           TRUE ~ "ERROR")

  word <- case_when(x == 0 ~ "Zeroth",
                    x == 1 ~ "Bottom",
                    x == 2 ~ "Second",
                    x == 3 ~ "Third",
                    x == 4 ~ "Fourth",
                    x == 5 ~ "Top")

  if (capitalize == TRUE) {
    tools::toTitleCase(word)
  } else {
    word
  }
}
```

@@

```{r chart1}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent_format(accuracy = 1)(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("More than One-Third of Early Millennials Will Likely See Their Living Standards Fall\nwhen They Retire"),
      subtitler("Percentage of adults unable to replace 75% of their preretirement earnings at age 70"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2.6, 2, 30, 1, 1))
```

<!-- ### 80% replacement rate -->

<!-- ```{r chart1b} -->
<!-- chart1 <- read_csv("data/figure1.csv") %>% -->
<!--   filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%")) %>% -->
<!--   filter(doby %in% cohorts) %>% -->
<!--   mutate(doby = rename_cohort(doby)) %>%   -->
<!--   group_by(doby) %>% -->
<!--   summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>% -->
<!--   ggplot(aes(doby, rep_rate_threshold)) + -->
<!--   geom_col() + -->
<!--   geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +     -->
<!--   scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), -->
<!--                      limits = c(0, 50)) + -->
<!--   labs(x = "Birth Cohort", -->
<!--        y = NULL) + -->
<!--   remove_ticks() + -->
<!--   remove_axis()    -->

<!-- # create the output plot -->
<!-- plotr(titler("Age 70 Percentage of People Who Fail to Replace 80% of Age 50-59 Earnings"), -->
<!--       chart1, -->
<!--       caption, -->
<!--       sourcer("DYNASIM4, ID963"), -->
<!--       heights = c(2, 30, 1, 1)) -->
<!-- ``` -->

<!-- ### 85% replacement rate -->

<!-- ```{r chart1c} -->
<!-- chart1 <- read_csv("data/figure1.csv") %>% -->
<!--   filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%")) %>% -->
<!--   filter(doby %in% cohorts) %>% -->
<!--   mutate(doby = rename_cohort(doby)) %>%   -->
<!--   group_by(doby) %>% -->
<!--   summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>% -->
<!--   ggplot(aes(doby, rep_rate_threshold)) + -->
<!--   geom_col() + -->
<!--   geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +     -->
<!--   scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), -->
<!--                      limits = c(0, 50)) + -->
<!--   labs(x = "Birth Cohort", -->
<!--        y = NULL) + -->
<!--   remove_ticks() + -->
<!--   remove_axis()    -->

<!-- # create the output plot -->
<!-- plotr(titler("Age 70 Percentage of People Who Fail to Replace 85% of Age 50-59 Earnings"), -->
<!--       chart1, -->
<!--       caption, -->
<!--       sourcer("DYNASIM4, ID963"), -->
<!--       heights = c(2, 30, 1, 1)) -->
<!-- ``` -->

<!-- ### 90% replacement rate -->

<!-- ```{r chart1d} -->
<!-- chart1 <- read_csv("data/figure1.csv") %>% -->
<!--   filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%", "85-90%")) %>% -->
<!--   filter(doby %in% cohorts) %>% -->
<!--   mutate(doby = rename_cohort(doby)) %>% -->
<!--   group_by(doby) %>% -->
<!--   summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>% -->
<!--   ggplot(aes(doby, rep_rate_threshold)) + -->
<!--   geom_col() + -->
<!--   geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +     -->
<!--   scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), -->
<!--                      limits = c(0, 50)) + -->
<!--   labs(x = "Birth Cohort", -->
<!--        y = NULL) + -->
<!--   remove_ticks() + -->
<!--   remove_axis()    -->

<!-- # create the output plot -->
<!-- plotr(titler("Age 70 Percentage of People Who Fail to Replace 90% of Age 50-59 Earnings"), -->
<!--       chart1, -->
<!--       caption, -->
<!--       sourcer("DYNASIM4, ID963"), -->
<!--       heights = c(1.8, 30, 1, 1)) -->
<!-- ``` -->

<!-- ### 100% replacement rate -->

<!-- ```{r chart1e} -->
<!-- chart1 <- read_csv("data/figure1.csv") %>% -->
<!--   filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%", "85-90%", "90-95%", "95-100%")) %>% -->
<!--   filter(doby %in% cohorts) %>% -->
<!--   mutate(doby = rename_cohort(doby)) %>% -->
<!--   group_by(doby) %>% -->
<!--   summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>% -->
<!--   ggplot(aes(doby, rep_rate_threshold)) + -->
<!--   geom_col() + -->
<!--   geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +     -->
<!--   scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), -->
<!--                      limits = c(0, 50)) + -->
<!--   labs(x = "Birth Cohort", -->
<!--        y = NULL) + -->
<!--   remove_ticks() + -->
<!--   remove_axis()    -->

<!-- # create the output plot -->
<!-- plotr(titler("Age 70 Percentage of People Who Fail to Replace 100% of Age 50-59 Earnings"), -->
<!--       chart1, -->
<!--       caption, -->
<!--       sourcer("DYNASIM4, ID963"), -->
<!--       heights = c(1.8, 30, 1, 1)) -->
<!-- ``` -->

@@

```{r chart2}
chart2 <- read_csv("data/figure2.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, ncharts_aftertax_income_P50)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::dollar(signif(ncharts_aftertax_income_P50, 3), largest_with_cents = 0)), 
            vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("A Typical Early Millennial Retiree Will Receive about 30 Percent More Income Than a\nTypical Retiree Born 40 Years Earlier"),
      subtitler("Median annual Social Security income at age 70 (constant 2018 dollars)"),
      chart2,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2.8, 1, 30, 1, 1))
```

@@

```{r, chart3}
chart3b <- read_csv("data/figure3b.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Male",
                       `2.Female` = "Female")) %>%  
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, Ownssb_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(round(Ownssb_P50, -2), largest_with_cents = 0)), 
            position = position_dodge(width = 0.75), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("For Early Millennials, Women’s Median Age-70 Social Security Benefits Will Rise to\n85 Percent of the Median for Men"),
      subtitler("Median annual Social Security income at age 70 (constant 2018 dollars)"),
      chart3b,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2.6, 2, 30, 1, 1))
```

@@

```{r chart4}
chart4 <- read_csv("data/figure4.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Male",
                       `2.Female` = "Female")) %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(male)) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, lifetime_earn_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(round(lifetime_earn_P50, -2), largest_with_cents = 0)), 
            position = position_dodge(width = 1), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Over Her Lifetime, a Typical Early Millennial Woman Will Earn More than Twice as Much\nas Her Pre-Boomer Counterpart"),
      subtitler("Median earnings from ages 25 to 69 (constant 2018 dollars)"),
      chart4,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2.6, 2, 30, 1, 1))
```

@@

# create the output plot
plotr(titler("Although Retirement Incomes Are Projected to Rise for People of Color, They\nWill Continue to Lag Far Behind Incomes for Non-Hispanic Whites"),
      subtitler("Median annual per capita after-tax family income at age 70 (thousands of constant 2018 dollars)"),
      chart6,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2.8, 1, 30, 1, 1))
```

## Chart 7: Social Security Is a Pillar of Retirement Security

@@

@@

quintile <- c("Bottom quintile", "Second quintile", "Third quintile", "Fourth quintile", "Top quintile")

chart7 <- read_csv("data/figure7.csv") %>%
  mutate(nchartQuin = paste(to_ordinal(nchartQuin), "quintile")) %>%
  mutate(nchartQuin = factor(nchartQuin, levels = quintile)) %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(doby, income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~nchartQuin) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# create the output plot
plotr(titler("Social Security Accounts for About 80 Percent of Income for Low-Income Retirees"),
      subtitler("Percent of age-70 per capita family income from Social Security by family income quintile"),
      chart7,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

```{r chart7alt}
chart7alt <- read_csv("data/figure7.csv") %>%
  mutate(nchartQuin = paste(to_ordinal(nchartQuin), "quintile")) %>%
  mutate(nchartQuin = factor(nchartQuin, levels = quintile)) %>%
  mutate(ss_share = PCssb_Mean / ncharts_aftertax_income_Mean) %>%
  filter(doby %in% cohorts) %>%
  select(nchartQuin, doby, ss_share) %>%
  ggplot(aes(doby, ss_share, fill = nchartQuin)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent_format(accuracy = 1)(ss_share)),
            position = position_dodge(width = 0.7),
            vjust = -0.8,
            hjust = 0.35) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Social Security Accounts for About 80 Percent of Income for Low-Income Retirees"),
      subtitler("Percent of age-70 per capita family income from Social Security by family income quintile"),
      chart7alt,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

@@

scheduled <- read_csv("data/figure1.csv") %>%
  mutate(law = "Current Social Security benefits continue")

payable <- read_csv("data/figure9.csv") %>%
  mutate(law = "Benefits cut 25%") %>%
  rename(ncharts_reprate = ncharts_reprate_payable)

chart9 <- bind_rows(scheduled, payable) %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby, law) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ungroup() %>%
  mutate(law = factor(law, levels = c("Current Social Security benefits continue", "Benefits cut 25%"))) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, rep_rate_threshold, fill = law)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::percent_format(accuracy = 1)(rep_rate_threshold / 100)), 
            vjust = -1,
            position = position_dodge(width = 0.8)) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Retirement Incomes May Fall Short for about 4 in 10 Early Millennials if Policymakers\nIgnore Social Security’s Financing Gap"),
      subtitler("Percentage of adults unable to replace 75% of their preretirement earnings at age 70 "),
      chart9,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2.8, 1, 30, 1, 1))
```

@@

```{r, chart12}
chart12 <- read_csv("data/figure12.csv") %>%
  filter(doby %in% cohorts) %>%
  rename(`Current Social Security benefits continue` = ncharts_pov_Mean, 
         `Benefits cut 25%` = ncharts_pov_payable_Mean) %>%
  mutate(doby = rename_cohort(doby)) %>% 
  gather(key = "law", value = "poverty", -doby, -Obs) %>%
  mutate(law = factor(law, levels = c("Current Social Security benefits continue", "Benefits cut 25%"))) %>%
  ggplot(aes(doby, poverty, fill = law)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::percent_format(accuracy = 0.1)(poverty)), 
            vjust = -1,
            position = position_dodge(width = 0.8)) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("A 25 Percent Social Security Benefit Cut Could Leave About One in Eight Gen X and\nEarly Millennial Retirees in Poverty"),
      subtitler("Percentage of adults with incomes below the federal poverty level at age 70 "),
      chart12,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2.6, 1, 30, 1, 1))
```

@@

## Chart 13 taxes

```{r, chart13}
